
\crefname{equation}{{\'e}q.}{{\'e}q.}%
\Crefname{equation}{{\'E}quation}{{\'E}quations}%
\crefname{figure}{fig.}{fig.}%
\Crefname{figure}{Figure}{Figures}%
\crefname{subfigure}{fig.}{fig.}%
\Crefname{subfigure}{Figure}{Figures}%
\crefname{table}{tab.}{tab.}%
\Crefname{table}{Tableau}{Tableaux}%
\crefname{subtable}{tab.}{tab.}%
\Crefname{subtable}{Tableau}{Tableaux}%
\crefname{page}{p.}{pp.}%
\Crefname{page}{Page}{Pages}%
\crefname{part}{part.}{part.}%
\Crefname{part}{Partie}{Parties}%
\crefname{chapter}{chap.}{chap.}%
\Crefname{chapter}{Chapitre}{Chapitres}%
\crefname{section}{sect.}{sect.}%
\Crefname{section}{Section}{Sections}%
\crefname{subsection}{sect.}{sect.}%
\Crefname{subsection}{Section}{Sections}%
\crefname{subsubsection}{sect.}{sect.}%
\Crefname{subsubsection}{Section}{Sections}%
\crefname{appendix}{ann.}{ann.}%
\Crefname{appendix}{Annexe}{Annexes}%
\crefname{subappendix}{ann.}{ann.}%
\Crefname{subappendix}{Annexe}{Annexes}%
\crefname{subsubappendix}{ann.}{ann.}%
\Crefname{subsubappendix}{Annexe}{Annexes}%
\crefname{subsubsubappendix}{ann.}{ann.}%
\Crefname{subsubsubappendix}{Annexe}{Annexes}%
\crefname{enumi}{pt.}{pts.}%
\Crefname{enumi}{Point}{Points}%
\crefname{enumii}{pt.}{pts.}%
\Crefname{enumii}{Point}{Points}%
\crefname{enumiii}{pt.}{pts.}%
\Crefname{enumiii}{Point}{Points}%
\crefname{enumiv}{pt.}{pts.}%
\Crefname{enumiv}{Point}{Points}%
\crefname{enumv}{pt.}{pts.}%
\Crefname{enumv}{Point}{Points}%
\crefname{footnote}{note}{notes}%
\Crefname{footnote}{Note}{Notes}%
\crefname{theorem}{th.}{th.}%
\Crefname{theorem}{Th\'eor\`eme}{Th\'eor\`emes}%
\crefname{lemma}{lemme}{lemmes}%
\Crefname{lemma}{Lemme}{Lemmes}%
\crefname{corollary}{corollaire}{corollaires}%
\Crefname{corollary}{Corollaire}{Corollaires}%
\crefname{proposition}{prop.}{prop.}%
\Crefname{proposition}{Proposition}{Propositions}%
\crefname{definition}{d\'ef.}{d\'ef.}%
\Crefname{definition}{D\'efinition}{D\'efinitions}%
\crefname{result}{r\'es.}{r\'es.}%
\Crefname{result}{R\'esultat}{R\'esultats}%
\crefname{example}{ex.}{ex.}%
\Crefname{example}{Exemple}{Exemples}%
\crefname{remark}{rq.}{rq.}%
\Crefname{remark}{Remarque}{Remarques}%
\crefname{note}{comm.}{comm.}%
\Crefname{note}{Commentaire}{Commentaires}%
\crefname{algorithm}{algo.}{algo.}%
\Crefname{algorithm}{Algorithme}{Algorithmes}%
\crefname{listing}{liste}{listes}%
\Crefname{listing}{Liste}{Listes}%
\crefname{line}{l.}{l.}%
\Crefname{line}{Ligne}{Lignes}%
